---
title: "Time Series Final Report"
author: "Sihan Zhuang"
format:
  html:
    toc: true
    number-sections: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
if (basename(getwd()) == "report") {
  setwd("..")
}
source("R/00_setup.R")
source("R/01_data_import.R")
```

# Research Question

How have Singapore's total fertility rate and total live-births evolved over time, and how well can short-horizon time series models forecast these demographic indicators?

# Data

The data are annual Singapore births and fertility rates from data.gov.sg and SingStat. The primary series used in this report are total fertility rate (TFR) and total live-births.

# Exploratory Analysis

```{r}
source("R/02_eda.R")
```

Summarise trend, cycles, stationarity, and transformations suggested by the data.

# Methods

```{r}
source("R/03_models.R")
```

Annual data have no seasonal frequency, so the main candidate models are non-seasonal ARIMA models. Total live-births are modelled on the log scale to stabilise proportional changes. The appendix reports viable models that were not selected.

# Results

Present the selected model, parameter estimates, diagnostics, and evidence supporting the model choice.

# Forecasting or Inference

```{r}
source("R/04_forecast_evaluation.R")
```

Report forecast accuracy and interpret short-horizon forecast uncertainty.

# Discussion

Discuss limitations, uncertainty, and whether the selected model answers the research question adequately.

# References

Add references used for data, methods, and model interpretation.
